---
title: "Toolbox for organoids analyses using drug screening and RNA-sequencing"
author: Pascal Belleau, Astrid Deschênes and Alexander Krasnitz
output:
    BiocStyle::html_document:
        number_sections: yes
        toc: true
    pkgdown:
      number_sections: yes
      as_is: true
urlcolor: darkred
linkcolor: darkred
vignette: >
    %\VignetteIndexEntry{Toolbox for organoids analyses using drug screening and RNA-sequencing}
    %\VignettePackage{OrganoidsToolBox}
    %\VignetteEngine{knitr::rmarkdown}
    %\VignetteEncoding{UTF-8}
---

```{r style, echo=FALSE, results='hide', warning=FALSE, message=FALSE}
BiocStyle::markdown()

suppressPackageStartupMessages({
    library(knitr)
    library(OrganoidsToolBox)
})

set.seed(121444)
```

<br />
**Package**: `r Rpackage("OrganoidsToolBox")`<br />
**Authors**: `r packageDescription("OrganoidsToolBox")[["Author"]]`<br />
**Version**: `r packageDescription("OrganoidsToolBox")$Version`<br />
**Compiled date**: `r Sys.Date()`<br />
**License**: `r packageDescription("OrganoidsToolBox")[["License"]]`<br />


# Licensing 

The `r Githubpkg("KrasnitzLab/OrganoidsToolBox")` package and the underlying 
`r Githubpkg("KrasnitzLab/OrganoidsToolBox")` code are distributed under  
the Artistic-2.0 license. You are free to use and 
redistribute this software.  

<br>
<br>

# Citing

If you use the **OrganoidsToolBox** package for a publication, we would ask 
you to cite the following:

> TODO 

<br>
<br>

# Introduction
TODO

<br>
<br>

# Installation

To install the latest version accessible on the 
[OrganoidsToolBox Github Website](https://github.com/KrasnitzLab/OrganoidsToolBox "OrganoidsToolBox Github Site"), 
the `r CRANpkg("devtools")` package is required.

```{r installDemo01, eval=FALSE}
## Load required package
library(devtools)

## Install the latest version of OrganoidsToolBox
devtools::install_github('KrasnitzLab/OrganoidsToolBox')
```

<br>
<br>


# Main Steps

TODO


<br>
<br>

# Session info

Here is the output of `sessionInfo()` on the system on which this document was 
compiled:

```{r sessionInfo, echo=FALSE}
sessionInfo()
```

<br>
<br>


# References

